Notes

### 2022-09-05 chapters/experiments.tex
Minor addition

A lot of minor things were tried, such as standardizing the regressors and/or the responses, smoothing the functional data, or transforming the values of \(\tau\) during sampling so that the domain was unconstrained. It is likely that some of these strategies would lead to better results in specific cases, but overall they did not improve the general performance of the prediction procedure.

>>>>

A lot of minor things were tried, such as standardizing the regressors and/or the responses, smoothing the functional data, changing the proposal of moves in the MCMC sampler, or transforming the values of \(\tau\) during sampling so that the domain was unconstrained. It is likely that some of these strategies would lead to better results in specific cases, but overall they did not improve the general performance of the prediction procedure.
